---
title: "Examples"
output: 
  rmarkdown::html_vignette:
    toc: true
bibliography: references.bib
link-citations: yes
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# An MNL design 
```{r eval = FALSE, file='examples/mnl-design.R'}
```

# An MNL design with interactions
```{r eval = FALSE, file='examples/mnl-design-with-interactions.R'}
```

# An MNL design with multiway interactions
```{r eval = FALSE, file='examples/mnl-design-with-multiway-interactions.R'}
```

# An MNL design with dummy-coded attributes 
```{r eval = FALSE, file='examples/mnl-design-dummy-coding.R'}
```

# An MNL design with specified level occurrences
```{r eval = FALSE, file='examples/mnl-design-random-with-specified-level-occurrence.R'}
```

# An MNL design with alternative specific attributes
```{r eval = FALSE, file='examples/mnl-design-with-alternative-specific-attributres.R'}
```

# An MNL design with Bayesian priors
```{r eval = FALSE, file='examples/mnl-design-bayesian-priors.R'}
```

# An MNL design with dummy-coded attributes, Bayesian priors, and restrictions on level occurrence
```{r eval = FALSE, file='examples/mnl-design-advanced.R'}
```

# An MNL design with a supplied candidate set
```{r eval = FALSE, file='examples/mnl-design-with-supplied-candidate-set.R'}
```

# An MNL design with specified explusions applied to the candidate set
```{r eval = FALSE, file='examples/mnl-design-with-exclusions.R'}
```

# An MNL design optimized for c-efficiency
```{r eval = FALSE, file='examples/mnl-c-efficiency.R'}
```
