---
title: "spdesignR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{spdesignR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(spdesignR)
```

# Introduction


# Syntax

## Estimation options
The package comes with a large number of estimation options. 

```{r}
estim_opts <- list(
  silent = FALSE,
  max_eval = 10000
)
```

## Specifying design options
The package allows for flexible designs. General design options are collected in the list `design_opts'. 

```{r, eval = FALSE}
design_opts <- list(
  S = 12,
  R = NA,
  model = "mnl",
  eff_crit = "d",
  blocks = 1
)
```





### Specifying the utility functions
The utility functions are specified as a list, where each list element is a character string defining the functional form of utility. 

For example, if you have two unlabeled alternatives, "alt_1" and "alt_2", you can specify the list of utility functions as follows:

```{r, eval = FALSE}
utility_funcs <- list(
  alt_1 = "beta_1[0.1] * x_1[0, 1] + beta_2[-0.1] * x_2[2, 4, 6, 8]",
  alt_2 = "beta_1 * x_1 + beta_2 * x_2"
)
```

It is important when specifying the utility functions that the parameter preceeds the attribute. The function that parses the utility expressions assumes that the parameter is to the left of the asterisk and the attribute to the right. Different attributes, or interaction terms, are separated by the addition symbol. 


### Specifying restrictions
